Treatment Outcome Visualization

### 2023-06-25 Treatment_Outcomes.Rmd
Crack at while loop.

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOS_pre = Day1_CUDOS
      ) %>%
  filter(!is.na(Days_complete_W)) %>%
  filter(!Days_complete_W == 0)

sum(is.na(Mothership_post$Days_complete_W))

#3. Then create df with CUDOS and CUXOS scores
  # Depression

@@

length(Mothership_post$Days_complete_W)

#4. Extract the valeues for each patient at their last day (length of stay), and create a CUDOS and CUXOS post score.

# Mothership_post2 <- Mothership_post %>%
#   mutate(
#     CUDOS_post = CUDOS_Score[cbind(seq_along(1:8610),CUDOS_Score$Days_complete_W)],
#     CUXOS_post = CUXOS_Score[cbind(seq_along(1:8610),CUXOS_Score$Days_complete_W)]
#   )

# CUDOS_Score2=CUDOS_Score[,2:41]
# CUXOS_Score2=CUXOS_Score[,2:41]

Mothership_post <- Mothership_post %>%
  mutate(
    CUDOS_post = CUDOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)],
    CUXOS_post = CUXOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)]
  )

####WTF
```

```{r}
#5. create new DF with Varaibles we want

@@

#6. Create long data frame

@@

#7. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

@@

@@

#3. Plot em

>>>>

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOS_pre = Day1_CUDOS
      ) %>%

#4. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_W)) %>%
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!Days_complete_1 > 40) %>%
  filter(!Days_complete_W == 0)

dim(Mothership_post)

#5. Then create df with CUDOS and CUXOS scores
  # Depression

@@

#6. Using incidences to extract values

Mothership_post <- Mothership_post %>%
  mutate(
    CUDOS_post = CUDOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)],
    CUXOS_post = CUXOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)]
  )

#7. create new DF with Varaibles we want

@@

#8. Create long data frame

@@

#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

@@

```{r, include=FALSE}
# Try to extract values using a while loop?

for (i in 1:nrow(CUDOS_Score)){
  while(is.na(CUDOS_Score[i,CUDOS_Score$Days_complete_W])){
    x = Days_complete_W -1
    post_days <- CUDOS_Score[i,(x)]
  }
}
```

@@
